---
title: "Updates on Eviction Court Cases"
author: "Justin Ho"
date: "2023-05-02"
output: html_document
---

```{r} 
library(knitr)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)

```

# Overview

This is to document the current state and updates for Eviction Court Cases as of **2023-05-02** and is divided into 6 sections

1. Documentation, Code Repository and Comprehensive Data

1. Classifications, Continuance and Writs

1. Geocoding

1. Demographics

1. Brute Force Scraping

1. Next Steps

------------------------------

## Documentation, Code Repository and Comprehensive Data
As an overview, the current plans in documentation, maintaining code and data repositories are going to be as follow

* **Code Repository** - *https://github.com/justinhjy1004/CourtCasesEviction*

* **Data Repository** - *https://www.dropbox.com/home/Justin_Research_Updates/CourtCasesEviction*

* **Documentation** -  *https://github.com/justinhjy1004/CourtCasesEviction/03_vizstat*

Note that the formal documentation is done within the GitHub repository in the directory *03_vizstat*. However, more general and detailed documentation should be found accompanied with the code, where contextual information (from the code) might matter significantly to understand the process.

------------------------------
## Classifications, Continuance and Writs

On the classifications, continuance and writs, a source of concern as I poured the data is the inconsistency in the words, phrases and **spelling** of certain terms. This is all based on the comprehensive list that was compiled by Professor Sullivan.

Specific problems that I want to document are

1. **Classifications** - There are cases where Contract-unspecified is part of the comprehensive list. Are they supposed to be considered eviction cases or was it a mistake. Furthermore, how important are the different classifications for Real Property?

1. **Continuance** - Differences in words under **ACTIONS** are found, where *'...the case is continued...'* and *'... continuance is issued...'*. In which case, I took the liberal approach and classified the case with continuance as long as words such as **continue and continuance** is found.

1. **Writs of Restitution** - For the writs of restitution, in some cases, the word restitution is misspelled. Hence, I classify the case where a writ is issued as long as the word *writ* is issued. This might not be a problem since the writ of restitution often corresponds with a Judgement.

```{r warning=FALSE}
cases <- read_csv("../02_cleaning/clean_all_cases.csv",show_col_types = FALSE)
classification <- as.data.frame(table(cases$CLASSIFICATION))
colnames(classification) <- c("Classification", "Frequency")
kable(classification)
```

Note that there is one cases where it is an unspecified contract case which I am not sure is an error.


----------------

## Geocoding